Location Classification on Tweets

### 2016-03-10 docs/paper.tex
for review

\subsection{Multi-Class Classification}
Random baseline compared with location names(as in the for 8 locations and

>>>>

\subsection{Multi-Class Classification}
Random baseline combined with obvious location names, for 8 locations, gives us a macro-averaged f1-score of  0.17. In our experiments with multi-class classification, we were able to improve this score to 150\% using SGDClassifier with different loss functions.
